Predictors of frog survival following translocations - analyses

### 2022-10-13 code/translocation_survival_exploratory.Rmd
Fix typo

* Hypothesized mechanism: Severity of winter follow translocation could affect frog condition and subsequent survival of translocated frogs in the first year following translocation. For example, a long winter following translocation could reduce survival in the first year. 
* No obvious effect of winter severity in year following translocation and frog survival.

>>>>

* Hypothesized mechanism: Severity of winter following translocation could affect frog condition and subsequent survival of translocated frogs in the first year following translocation. For example, a long winter following translocation could reduce survival in the first year. 
* No obvious effect of winter severity in year following translocation and frog survival.
